Automatically Splitting a Two-Stage Lambda Calculus

### 2015-07-10 paper/examples.tex
Fix a bunch of references to "passes" in the graphics section.

Programs featuring staged structure are particularly important in real-time
computer graphics since modern graphics architectures \emph{require} that
graphics computations be organized into distinct {\em passes} which perform
increasingly fine-grained computations (e.g., per object, per screen region,
per pixel) where many computations in later passes use the
results from a single computation in an earlier pass\,\cite{OpenGL4Spec}.

While performant, programming with explicit passes results in complex
code where invariants must hold across different passes, and local
changes for one pass may require changes to other passes to ``plumb''
its inputs through all upstream passes. Thus, requiring manual
separation of passes breaks key programming abstractions such as
composition and modularity.  Graphics researchers therefore have
suggested using explicitly staged programs
\,\cite{Proudfoot:2001,Foley:2011,He:2014} to express logic related to
a single application concern conveniently as a single staged function
(referred to as a pipeline program)\,\cite{Foley:2011}.

>>>>

Programs featuring staged structure are particularly important in
real-time computer graphics since modern graphics architectures
\emph{require} that graphics computations be organized into a pipeline
of stages which perform increasingly fine-grained computations (e.g.,
per object, per screen region, per pixel). Many computations in later
stages use the results from a single computation in an earlier
stage\,\cite{OpenGL4Spec}.

While performant, manually partitioning programs by stage results in
complex code where invariants must hold across different stages, and
local changes to the logic of one stage may require changes to that of
upstream stages other stages to ``plumb'' its inputs through the
pipeline.  Thus, manual separation of programs by stage breaks key
programming abstractions such as composition and modularity.  Graphics
researchers therefore have suggested using mixed-staged programs
\,\cite{Proudfoot:2001,Foley:2011,He:2014} to express logic related to
a single application concern conveniently as a single staged function
(referred to as a pipeline program)\,\cite{Foley:2011}.
